### 2020-02-24 ChapterBackground/chapterBackground.tex
Updated: References and TODOs in Online Gaming Background

@@

@@

@@

\subsubsection{Distributed server}
Distributed server or Multi-Server architectures use multiple servers and the computational workload is divided between the servers. This can be achieved in one of two ways, either through `shards' or through division of the game world.

In the `shards' method, complete and separate instances of the game world exist, each maintained by one serve. Each server is responsible for a different set of clients. The game can be scaled through the introduction of more servers, supporting more clients. However, as each instance of the game world is separate, there can be no interaction in the game world between players on different shards.

In the game world division method, there is a single instance of the game world and the workload is distributed either through each server being responsible for a region or a set of players. Division methods are discussed further in \ref{distrubted_virtual_env}. 
a single server can be overloaded if the workload is too high for example a large number of players in a region being managed by a single server. Dynamic load-balancing schemes can be employed to improve distribution between servers. The disadvantage of this approach is the need for complex hand-offs when players migrate or interact between servers and can lead to consistency problems between servers as latency will always exist between servers.

The distributed server approach enables scalability as more servers can be utilised, allowing support for more players. However, depending on workload distribution, more problems are introduced. Fault-tolerance is potentially higher than a single server solution, even if no backup system is employed, as only players connected to the failing server will be affected.

% Game can be divided up in very different ways. Shards, regions (migratory), player-based (non-migratory)
% One server can overloaded if the workload is too high in one region
% Dynamic load-balancing schemes can be employed
% Hand-off between regions is complicated for players, let alone real-time physics

@@

>>>>

%Strong Consistency
%Weak Consistency
%2 of 3, availability, network partitioning, consistency
%An Enhanced Dead Reckoning Model for Physics-Aware Multiplayer Computer Games
%Peer-to-Peer Architectures for Massively Multiplayer Online Games: A Survey
%TODO: Talk about consistency in Proposed Solution

@@

% Latency and scalability: a survey of issues and techniques for supporting networked games
% Synchronization Technique - Lock-step
% Optimistic Technique
%TODO: Talk about latency compensation in Proposed Solution

@@

%MANAGING LATENCY AND FAIRNESS IN NETWORKED GAMES

@@

\subsubsection{Distributed server}
% TODO: More references for this
Distributed server or Multi-Server architectures use multiple servers and the computational workload is divided between the servers. This can be achieved in one of two ways, either through `shards' or through division of the game world.

In the `shards' method, complete and separate instances of the game world exist, each maintained by one serve. Each server is responsible for a different set of clients. The game can be scaled through the introduction of more servers, supporting more clients. However, as each instance of the game world is separate, there can be no interaction in the game world between players on different shards \cite{P2PSurvey}.

In the game world division method, there is a single instance of the game world and the workload is distributed either through each server being responsible for a region or a set of players. Division methods are discussed further in \ref{distrubted_virtual_env}. 
a single server can be overloaded if the workload is too high, for example, by a large number of players in a region being managed by a single server. Dynamic load-balancing schemes can be employed to improve distribution between servers. The disadvantage of this approach is the need for complex hand-offs when players migrate or interact between servers and can lead to consistency problems between servers as latency will always exist between servers \cite{P2PSurvey}.

The distributed server approach enables scalability as more servers can be utilised, allowing support for more players. However, depending on workload distribution, more problems are introduced. Fault-tolerance is potentially higher than a single server solution, even if no backup system is employed, as only players connected to the failing server will be affected \cite{P2PSurvey}.

%TODO: Mention cost? Persistent games?

@@

%TODO: Mention delta-update techniques, advantages and problems created
